Timeliness of security updates for Android

### 2014-08-06 securityupdates.tex
Move subsection on DA data validity after the exciting results from it

\documentclass[conference,a4paper,twoside]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{hyperref}
\RequirePackage[date=terse,isbn=true,doi=true,url=false,urldate=iso8601,maxbibnames=9,backref=false,backend=bibtex]{biblatex}
\addbibresource{securityupdates.bib}
\renewcommand{\bibfont}{\small}

@@

The data from Device Analyzer (DA) we want to use to investigate the proportion of devices exposed to different vulnerabilities is the OS version.
Unfortunately there is no authoritative source of OS version information and so we cannot check directly whether our data is representative.
However Google has published API version information every month since December 2009 and we have collated this information.\footnote{\url{https://www.cl.cam.ac.uk/~drt24/android/versiondistribution/}}
While API versions are too coarse grained to use for security update detection they are closely related to OS versions and so if the DA data on API versions is similar to the Google Data on API versions then the DA data on OS versions should be representative.
Figure \ref{fig:play_api} shows the data from Google and Figure \ref{fig:da_api} shows the data from Device Analyzer and they appear similar.
Figure \ref{fig:da_gp_comp_diff} shows the difference between Figures \ref{fig:play_api} and \ref{fig:da_api}, normalising for days since the API version was released.
It shows that the Device Analyzer data systematically overestimates the prevalence of new API versions and underestimates the prevalence of old API versions.
This means that the OS version information from Device Analyzer is likely to be overestimating the prevalence of new OS versions and hence our results are a conservative estimate of the security of Android.
%TODO we want a statistical metric to claim this strongly with.
\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/googleplayapi}
 \caption{Google Play data on proportion of devices running different Android API versions}
 \label{fig:play_api}
\end{figure}
\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/norm_api_gpcomp}
 \caption{Device Analyzer data on proportion of devices running different Android API versions}
 \label{fig:da_api}
\end{figure}
\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/api_gpcomp_rdiff}
 \caption{Difference between Device Analyzer and Google Play data on the proportion of devices running different Android API versions}
 \label{fig:da_gp_comp_diff}
\end{figure}

This allows us to have confidence in the OS version information.
Figure \ref{fig:norm_os} shows the proportion of devices in the Device Analyzer data running different versions of Android each day.
It shows how old versions are gradually replaced by new ones, the long tail of devices which do not see updates to more recent versions and the fluctuation in the number of devices in the data.
\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/da_norm_os}
 \caption{Android versions in Device Analyzer data over time}
 \label{fig:norm_os}
\end{figure}

@@

>>>>

\documentclass[conference,a4paper,twoside]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{hyperref}
\usepackage{subcaption}
\RequirePackage[date=terse,isbn=true,doi=true,url=false,urldate=iso8601,maxbibnames=9,backref=false,backend=bibtex]{biblatex}
\addbibresource{securityupdates.bib}
\renewcommand{\bibfont}{\small}

@@

The proportion of devices in the Device Analyzer data running different versions of Android each day is shown in Figure~\ref{fig:norm_os}.
It shows how old versions are gradually replaced by new ones, the long tail of devices which do not see updates to more recent versions and the fluctuation in the number of devices in the data.
We verify the validity of this data in \S\ref{sec:representative}.
\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/da_norm_os}
 \caption{Android versions in Device Analyzer data over time}
 \label{fig:norm_os}
\end{figure}

@@

\subsection{The Device Analyzer data gives a conservative estimate of the Android version distribution}
\label{sec:representative}
\begin{figure}
 \centering
 \begin{subfigure}[b]{\columnwidth}
 \includegraphics[width=\columnwidth]{figures/googleplayapi}
 \caption{Google Play data on proportion of devices running different Android API versions}
 \label{fig:play_api}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
 \includegraphics[width=\columnwidth]{figures/norm_api_gpcomp}
 \caption{Device Analyzer data on proportion of devices running different Android API versions}
 \label{fig:da_api}
\end{subfigure}
\caption{Monthly Android API version data}
\end{figure}
\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/api_gpcomp_rdiff}
 \caption{Difference between Device Analyzer and Google Play data on the proportion of devices running different Android API versions}
 \label{fig:da_gp_comp_diff}
\end{figure}
The data from Device Analyzer (DA) we used to investigate the proportion of devices exposed to different vulnerabilities is the OS version.
Unfortunately there is no authoritative source of OS version information and so we cannot check directly whether our data is representative.
However Google has published API version information every month since December 2009 and we have collated this information.\footnote{\url{https://www.cl.cam.ac.uk/~drt24/android/versiondistribution/}}
While API versions are too coarse grained to use for security update detection they are closely related to OS versions and so if the DA data on API versions is similar to the Google Data on API versions then the DA data on OS versions should be representative.
Figure \ref{fig:play_api} shows the data from Google and Figure \ref{fig:da_api} shows the data from Device Analyzer and they appear similar.
Figure \ref{fig:da_gp_comp_diff} shows the difference between Figures \ref{fig:play_api} and \ref{fig:da_api}, normalising for days since the API version was released.
It shows that the Device Analyzer data systematically overestimates the prevalence of new API versions and underestimates the prevalence of old API versions.
This means that the OS version information from Device Analyzer is likely to be overestimating the prevalence of new OS versions and hence our results are a conservative estimate of the security of Android.
%TODO we want a statistical metric to claim this strongly with.
This allows us to have confidence in the OS version information.
